CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-17 codecheck-paper.tex
working through the register, adding bibliographies...

DANIEL: COULD YOU DO THIS?
This example workflow leaves sufficient room for different
implementations of this process. There are several aspects that can be
considered:

@@

\textbf{2. Communication between humans is key.} Some code may just work
without any interaction (e.g.~Manuel's certificate); however, more often
there are hidden dependencies that need to be found, or revised software
installations. Allowing the codechecker and human to communicate
directly and openly with each other should make this process as
constructive as possible. We feel that routing this conversation
(possibly anonymously) through a publisher would slow things down and
reduce the chances for community bulding.

@@

We would like to briefly highlight three examples here.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Gigascience -- our first paper. Only visualisation, not machine
  learning (which would have taken sseveral days of compute time).
\item
  report 9 -- covid model of UK lockdown model.
\item
  Geoscience (add 6 for Agile).
\end{enumerate}

@@

  \begin{tabular}{lllp{9cm}}  \toprule
    Certificate & Ref & Research area & Description \\ \midrule
    2020-001 & \cite{cert-2020-001} & Machine learning & CODECHECK undertaken post acceptance of manuscript and before its publication in \textit{Gigascience} \cite{Piccolo2020-lo}.
    \\ 
    2020-002 & \cite{cert-2020-002} & neuroscience &
    Paper from 1997 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
    \\
    2020-003 & \cite{cert-2020-003} & neuroscience &
    Classic paper from 1982 on  models of associative memory \cite{Hopfield1982-mz}. \\
    2020-004 & \cite{cert-2020-004} & area & barto \\
    2020-005 & \cite{cert-2020-005} & area & Larisch \\
    2020-006 & \cite{cert-2020-006} & area & Detorakis \\
    2020-007 & \cite{cert-2020-007} & area & in progress \\
    2020-008 & \cite{cert-2020-008} & Covid & covid-uk Davies \\
    2020-009 & \cite{cert-2020-009} & Covid &  tracing \\
    2020-010 & \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011 & \cite{cert-2020-011} & Covid &  nature europe \\
    2020-012 & \cite{cert-2020-012} & Covid &  USA Covid modelling \cite{Unwin2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.}
  \label{tab:register}
\end{table}

@@

\begin{itemize}
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in juornals.
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\end{itemize}

>>>>

DANIEL: COULD YOU DO THIS SECTION ON DIMENSIONS?
This example workflow leaves sufficient room for different
implementations of this process. There are several aspects that can be
considered:

@@

\textbf{2. Communication between humans is key.} Some code may just work
without any interaction (e.g.~Manuel's certificate); however, more often
there are hidden dependencies that need to be found, or revised software
installations. Allowing the codechecker and human to communicate
directly and openly with each other should make this process as
constructive as possible. We feel that routing this conversation
(possibly anonymously) through a publisher would slow things down and
reduce the chances for community building.

@@

The bulk of the certificates fall into three themes: (1) `classic'
papers from computational neuroscience (2) Covid modelling preprints
(3) AGILE.  We would like to briefly highlight three examples here.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Gigascience -- our first paper. Only visualisation, not machine
  learning (which would have taken sseveral days of compute time).
\item
  report 9 -- covid model of UK lockdown model -- unlike many claims
  in the popular media at the time, the model was reproducible
  [NOORDEN news piece]. 
\item
  Manuel's certificate -- approached us as he requested a certificate
  as paper was entering peer review.
\end{enumerate}

(DANIEL: say something about the Agile bundle, and the origins?)

@@

  \begin{tabular}{lllp{9cm}} \toprule Certificate & Ref & Research
    area & Description \\ \midrule 2020-001 & \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}.
    \\
    2020-002 & \cite{cert-2020-002} & neuroscience & Paper from 1997
                                                     showing
                                                     unsupervised
                                                     learning from
                                                     natural images
                                                     \cite{Hancock1992-mp}.
    \\
    2020-003 & \cite{cert-2020-003} & neuroscience &
                                                     Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004 & \cite{cert-2020-004} & area & Barto \\
    2020-005 & \cite{cert-2020-005} & area & Larisch \\
    2020-006 & \cite{cert-2020-006} & area & Detorakis \\
    2020-007 & \cite{cert-2020-007} & area & in progress \\
    2020-008 & \cite{cert-2020-008} & Covid & Modelling of
    interventions on Covid  cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009 & \cite{cert-2020-009} & Covid &  tracing \\
    2020-010 & \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011 & \cite{cert-2020-011} & Covid & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012 & \cite{cert-2020-012} & Covid &   Modelling of Covid spread across the USA; preprint currently review \cite{Unwin2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.  SJE
to complete...}
  \label{tab:register}
\end{table}

@@

\begin{itemize}
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\end{itemize}
